---
title: "Visualization I"
author: "Elaine Yanxi Chen"
date: 2022-09-29
output: 
  github_document
    

    
---

```{r, echo = FALSE}
library(tidyverse)
library(ggridges)
```

Copy code from the course website to download data.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df %>% view
```

## Scatterplot

Let's make a scatterplot

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + geom_point()
```

Let's make the same scatterplot but different.

```{r}
weather_df %>%
  drop_na() %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point()
```

Can save ggplot objects and continue to print or edit. Can have a base figure and have different type of figures superimpose on top of it. Save and export explicitly. 

```{r}
weather_scatterplot =
  weather_df %>%
  drop_na() %>% 
  ggplot(aes(x = tmin, y = tmax)) 

weather_scatterplot +
  geom_point()
```

## Let's fancy this up a bit

Want colour: mapping variable to aesthetics

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, colour = name)) +
  geom_point()
```

Can define aesthetics mapping for specific geometry.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(colour = name))
```

Add in a new aesthetics.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_point(aes(colour = name)) +
  geom_smooth()
```

But this only gives one smooth line for all three different groups. We can change that.

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, colour = name)) +
  geom_point() +
  geom_smooth()
```