---
title: "Simple document"
author: "Elaine Yanxi Chen"
date: 2022-09-13
output: 
  github_document
    

    
---

```{r}
library(tidyverse)
```

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

**for bold**
_italized_

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.
Can regulate the digits in `r round(mean(samp), 2)`

In-line r code, used very rarely, but useful

# Section 3

## Plot from last time 

This is going to make a plot. First I generate a dataframe, then use `ggplot` to
make a scatterplot.

Keystroke for creating a code chunk: Option + Command + I 



```{r}
plot_df = 
  tibble(
    x = rnorm(n = 1000),
    y = 1 + 2 * x + rnorm(n = 1000)
  )
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

## Plot for learning Assessment

```{r Learning Assessment 1}
library(tidyverse)

la_df =
  tibble(
    norm = rnorm(n = 500, mean = 1),
    logical = norm > 0,
    abs_norm = abs(norm)
  )


median_norm = median(pull(la_df, norm))
```

The median of the variable containing absolute values is `r round(median_norm, digits = 2)`

Here's a list:

* List item 1
* List item 2

Here is a list for the learning assessment:

* The mean of the original random sample is `r mean(pull(la_df, norm))`

* The median of the sample is `r median(pull(la_df, norm))`

* The standard deviation of the sample is `r sd(pull(la_df, norm))`
